\documentclass[11pt,a4paper,titlepage,final,table]{article}

% Meta-Commands
\input{./meta}  
% STY-Datei mit Package- und Command-Definitionen   		
\usepackage{./hbrs-inf}


\begin{document}
\maketitle
\clearpage
\pagenumbering{roman}
\setcounter{page}{2}
\pagestyle{plain}
\parskip 0.5em

% Inhaltsverzeichnis
%\setcounter{tocdepth}{2}
%\tableofcontents
%\clearpage

% Abbildungsverzeichnis
%\listoffigures
%\clearpage

% Tabellenverzeichnis
%\listoftables
%\clearpage


%\clearpage
\pagenumbering{arabic}

\lstset{
	basicstyle=\ttfamily\small,
	keywordstyle=\bfseries,
	language=[Sharp]C
}

% Insert sections here
\section{Introduction}
In this chapter, goals of the research project are described and contributors are introduced.
\input{./section/subsection/goals}
\input{./section/subsection/contributors}

\section{Related Work}
In the first sub section of this chapter, an overview of the literature in our field and context is provided.
In the second sub section of this chapter, our previous studies are described.
\input{./section/subsection/literature}
\input{./section/subsection/previous_studies}

\section{Planned Technology and Artistic Concept}
In this chapter, our concepts are described along with potential research questions.
Moreover, technical risks are considered, whereby we also state our solutions to mitigate the risks.
\input{./section/subsection/system_design}
\input{./section/subsection/technical_development}
\input{./section/subsection/technical_risks}
\input{./section/subsection/potential_research_questions}
\input{./section/subsection/development_goals}

\section{Materials and Methods}
In this chapter, required hardware and applied methods are discussed.
\input{./section/subsection/materials}
\input{./section/subsection/methods}

\section{Project Planning}
In this chapter, our initial project plan is provided, which applies at the beginning of the project and which is binding.
\input{./section/subsection/work_packages}
\input{./section/subsection/milestones}
\input{./section/subsection/responsibilities}

\newpage

%Literaturverzeichnis
\begin{thebibliography}{2}
\bibitem{1}
Polsley et al. https://link.springer.com/article/10.1007/s40593-021-00279-7, 2021
\bibitem{2}
Beltzung et al https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9945213/, 2023
\bibitem{3}
Google Creative Labs. https://experiments.withgoogle.com/quick-draw, 2017
\bibitem{4}
Meta. https://about.fb.com/news/2021/12/using-ai-to-animate-childrens-drawings/, 2021
\bibitem{5}
Shakeri. https://dl.acm.org/doi/abs/10.1145/3462204.3481771 , 2021
\bibitem{6}
C. Zhang et al. https://dl.acm.org/doi/abs/10.1145/3491102.3501914, 2022
\bibitem{7}
Z. Zhang et al. https://dl.acm.org/doi/abs/10.1145/3491102.3517479, 2022
\bibitem{8}R. Brunelli. Template Matching Techniques in Computer Vision: Theory and Practice, Wiley, ISBN 978-0-470-51706-2, 2009
\bibitem{9}J. Canny. A Computational Approach To Edge Detection, IEEE Transactions on Pattern Analysis and Machine Intelligence, 1986
\bibitem{10}
Girshick, R., Donahue, J., Darrell, T., and Malik, J. Rich feature hierarchies
for accurate object detection and semantic segmentation. CVPR, 2014
\end{thebibliography}

\end{document}
